Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-17 ms.tex
Changing to the newest emulateapj.
Adding AMR scaling section with an associated table.  I still need to add some references in this section.  Fixing some undefined and multiple labels and making the UVB table wider and spaced nicely.
Rearranging sections.

%\documentclass[10pt,preprint]{aastex}  % for e-submission to ApJ
%\documentclass[12pt,preprint2]{aastex}  % for e-submission to ApJ - two column
\documentclass[onecolumn]{emulateapj}  % this makes everything look like ApJ

@@

% Paper Outline  (last updated January 18, 2013)
%
% 1.  Introduction
% 2.  Physical equations and overview
%   2.1 Physical equations
%   2.2 Overview of numerical methods
% 3.  Numerical methods
%   3.1   AMR
%   3.2.  Hydro: Godunov (PPM)
%   3.3   Hydro: Godunov (MUSCL)
%   3.4   Hydro: Finite difference (ZEUS)
%   3.5   MHD: Dedner
%   3.6   MHD: CT
%   3.7   Gravity
%   3.8   Particle Integration
%   3.9.  Chemistry
%   3.10 Cooling
%   3.11 Radiation: Homogeneous
%   3.12 Radiation: ray-tracing
%   3.13 Radiation: FLD
%   3.14 Thermal conduction
%   3.15 Star formation & Feedback
%   3.16 Timestep constraints
%   3.17 Analysis
% 4. Code tests
%   4.1 Verifying and Validating the Enzo code
%   4.2 Representative test problems
% 5. Parallelism 
%   5.1 Parallel strategy 
%   5.2 Parallel performance 
% 6. Code development methodology
% 7. Conclusions
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%% Section: numerical methods
\section{Numerical Methods}
\label{sec.methods}

We now describe each of the numerical methods in detail.  The
structure of this section mirrors that of Section~\ref{sec.overview},
in which each method was briefly described.

\input{numerical-amr}
\input{numerical-ppm}
\input{numerical-muscl} % new
\input{numerical-mhd-dedner} % new (combined with muscl)
\input{numerical-mhd-ct}  % new
\input{numerical-zeus}
\input{numerical-gravity}
\input{numerical-particle}
\input{numerical-chemistry}
\input{numerical-cooling} % new
\input{numerical-radiation-homogeneous} % new
\input{numerical-radiation-raytracing} % new
\input{numerical-radiation-fld} % new
\input{numerical-conduction} % new
\input{numerical-starformation}
\input{numerical-timestep}
\input{numerical-analysis} % new

@@

%% Section: code development methodology
\input{development} % new

%% Section: conclusions
\input{conclusions}  % new

@@

\input{appendix}  % new

>>>>

%\documentclass[10pt,preprint]{aastex}  % for e-submission to ApJ
%\documentclass[12pt,preprint2]{aastex}  % for e-submission to ApJ - two column
\documentclass[onecolumn,iop]{emulateapj}  % this makes everything look like ApJ

@@

% Paper Outline  (last updated January 18, 2013)
%
% 1.  Introduction
% 2.  Physical equations and overview
%   2.1 Physical equations
%   2.2 Overview of numerical methods
% 3.  Numerical methods   %%%%%% THIS IS NOW A BUNCH OF DIFFERENT SECTIONS
%   3.1   AMR
%   3.2.  Hydro: Godunov (PPM)
%   3.3   Hydro: Godunov (MUSCL)
%   3.4   Hydro: Finite difference (ZEUS)
%   3.5   MHD: Dedner
%   3.6   MHD: CT
%   3.7   Gravity
%   3.8   Particle Integration
%   3.9.  Chemistry
%   3.10 Cooling
%   3.11 Radiation: Homogeneous
%   3.12 Radiation: ray-tracing
%   3.13 Radiation: FLD
%   3.14 Thermal conduction
%   3.15 Star formation & Feedback
%   3.16 Timestep constraints
%   3.17 Analysis
% 4. Code tests
%   4.1 Verifying and Validating the Enzo code
%   4.2 Representative test problems
% 5. Parallelism 
%   5.1 Parallel strategy 
%   5.2 Parallel performance 
% 6. Code development methodology
% 7. Conclusions
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%% Section: numerical methods
% \section{Numerical Methods}
% \label{sec.methods}

% We now describe each of the numerical methods in detail.  The
% structure of this section mirrors that of Section~\ref{sec.overview},
% in which each method was briefly described.

\input{numerical-amr}

\section{Fluid methods}
\label{sec:fluids}

\input{numerical-ppm}
%\input{numerical-muscl} 
\input{numerical-mhd-dedner}  % includes MUSCL and Dedner
\input{numerical-mhd-ct}  
\input{numerical-zeus}

\section{Gravity and N-body}
\label{sec:allgrav}
\input{numerical-gravity}
\input{numerical-particle}

\section{Microphysics}
\label{sec:microphysics}
\input{numerical-chemistry}
\input{numerical-cooling}

\section{Radiation}
\label{sec:allrad}
\input{numerical-radiation-homogeneous} 
\input{numerical-radiation-raytracing} 
\input{numerical-radiation-fld}

\section{Other physics}
\label{sec:otherphys}
\input{numerical-conduction} 
\input{numerical-starformation}

% this is its own section
\input{numerical-timestep}

% this is its own section
\input{numerical-analysis}

@@

%% Section: code development methodology
\input{development}

%% Section: conclusions
\input{conclusions}

@@

\input{appendix}
